Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-11-22 MHCpaper/MHCsupp.tex
scan figs

We see that, for most parameter values, such models do not reproduce the observed learning impairment with enhanced plasticity.
In some cases a very small learning impairment was seen, but these occurred at extreme parameter values where floating point precision could become an issue.

\begin{figure}
  \centering
  \begin{myenuma}
    \item\aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly_scan.eps}}\label{fig:pooled_bal}
    \item\aligntop{\includegraphics[width=0.29\linewidth]{cascade_scan.eps}}\label{fig:cascade_bal}
    \item\aligntop{\includegraphics[width=0.29\linewidth]{nonuni_scan.eps}}\label{fig:nonuni_bal}
  \end{myenuma}
  \caption{Difference in initial learning rate in wild-type and \KO\ models, without gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 7/5 relevant parameters (see \protect\hyperlink{par:bal_scan}{text}).
  We see that this quantity is usually negative, whereas it was positive in the experiments.
  The exceptions are very small, and tend to occur at extreme parameter values where rounding errors may occur.
  }\label{fig:bal}
\end{figure}

>>>>

We see that, for most parameter values, such models do not reproduce the observed learning impairment with enhanced plasticity.
In some cases a very small learning impairment was seen ($\CO(10^{-5})$), but these occurred at extreme parameter values where the tolerances used in fitting the potentiation parameter could have a noticeable impact.

\begin{figure}
  \centering
  \begin{myenuma}
    \item\aligntop{\includegraphics[width=0.29\linewidth]{pooled_scan.eps}}\label{fig:pooled_bal}
    \item\aligntop{\includegraphics[width=0.29\linewidth]{cascade_scan.eps}}\label{fig:cascade_bal}
    \item\aligntop{\includegraphics[width=0.29\linewidth]{nonuni_scan.eps}}\label{fig:nonuni_bal}
  \end{myenuma}
  \caption{Difference in initial learning rate in wild-type and \KO\ models, without gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 7/5 relevant parameters (see \protect\hyperlink{par:bal_scan}{text}).
  We see that this quantity is usually negative, whereas it was positive in the experiments.
  The exceptions are very small, $\CO(10^{-5})$, and tend to occur at extreme parameter values where the accuracy of fitting the potentiation parameter could become an issue.
  }\label{fig:bal}
\end{figure}
